The Iterative Signature Algorithm for Gene Expression data

### 2009-07-15 eisa/inst/doc/EISA_tutorial.Rnw
eisa vignette update, use profile.plot instead of parallelCoordinates.

Profile plots visualize the difference between the genes (or samples)
in the modules and the rest of the expression data. A profile plot
contains a line plot for every single gene (or sample) and the genes
that belong to the module have a different color, see
Fig.~\ref{fig:parallel}.
<<parallel.pre,echo=FALSE,results=hide>>=
CairoPNG("parallel.png", 400, 400 )
@ 
<<parallel>>=
ex <- samp.exprs(isa.normalize(ALL[featureNames(modules),]))
parallelCoordinates(ex, Bc, number=2, pch=NA)
@
<<parallel.post,echo=FALSE,results=hide>>=
dev.off()
@ 
\begin{figure}
\centering
\includegraphics[width=0.7\textwidth]{parallel}
\caption{Profile plots for the first bicluster found by ISA.}
\label{fig:parallel}
\end{figure}

>>>>

Profile plots visualize the difference between the genes (or samples)
in the modules and the rest of the expression data. A profile plot
contains a line plot for every single gene (or sample) and the genes
that belong to the module have a different color, see
Fig.~\ref{fig:parallel}.
<<parallel.pre,echo=FALSE,results=hide>>=
CairoPNG("parallel.png", 400, 400 )
@ 
<<parallel>>=
profile.plot(modules, 2, ALL, plot="both")
@
<<parallel.post,echo=FALSE,results=hide>>=
dev.off()
@ 
\begin{figure}
\centering
\includegraphics[width=0.7\textwidth]{parallel}
\caption{Profile plots for the second bicluster found by ISA.}
\label{fig:parallel}
\end{figure}

The \Rfunction{profile.plot} function has several options to set the
plot colors and styles, please see the manual for the details. This
function was inspired by the \Rfunction{parallelCoordinates} function
in the \Rpackage{biclust} package.
